Supplementary Information

### 2015-09-04 manuscript/supplement.tex
cosmetic changes

    None of our models were greatly affected by the removal of any single food web
    or by the removal of a set of webs compiled by a common researcher (or group of
    researchers).
    Estimates of coefficients from all jackknifed datasets were extremely
    similar (Figs.~\ref{LS_web},\ref{Gen_web},\ref{Vul_web},\ref{LS_auth},\ref{Gen_auth},\ref{Vul_auth}). 
    We are therefore very confident that, while there are undoubtedly differences 
    in the methods used to compile food webs, these differences do not explain the trends we report in this study.

@@

    \begin{figure}[!h]
    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/LS_author.eps}}
    \caption{Estimates of the coefficients for scaling of link density with species richness
    in equation 5 (main text) do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the pseudovalues for each coefficient
    in the equation after the removal of all webs compiled by each author (or set of authors where
    multiple authors compiled identical sets of webs) in the dataset. Authors
    who compiled only a single web were jackknifed as part of the by-web jackknife.
    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line, and
    the number of webs removed in each jackknife is given in parentheses.}
    \label{LS_web}
    \end{figure}

@@

    \begin{figure}[!h]
    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/Gen_author.eps}}
    \caption{Estimates of the coefficients for scaling of generality with species richness
    (see equation 5, main text) do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the pseudovalues for each coefficient
    in the equation after the removal of all webs compiled by each author (or set of authors where
    multiple authors compiled identical sets of webs) in the dataset. Authors
    who compiled only a single web were jackknifed as part of the by-web jackknife.
    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line, and
    the number of webs removed in each jackknife is given in parentheses.}
    \label{Gen_web}
    \end{figure}

@@

    \begin{figure}[!h]
    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/Vul_author.eps}}
    \caption{Estimates of the coefficients for the scaling of vulnerability with species richness
    (see equation 5, main text) do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the pseudovalues for each coefficient
    in the equation after the removal of all webs compiled by each author (or set of authors where
    multiple authors compiled identical sets of webs) in the dataset. Authors
    who compiled only a single web were jackknifed as part of the by-web jackknife.
    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line, and
    the number of webs removed in each jackknife is given in parentheses.}
    \label{Vul_web}
    \end{figure}

@@

\begin{figure}[!h]
\centerline{\includegraphics*[height=.75\textheight]{Figures/by_TL/scaling_with_S/proportions/TL_fitlines_nonts_observed.eps}}
\caption{Scaling relationships for link density, generality, 
and vulnerability relative to the proportions of basal resources, intermediate consumers, and top predators in a food web. 
For each relationship, we show observed values (white circles) and 
a simplified form of the scaling relationship described in equation 2 (\emph{Main Text}), neglecting 
any effects of habitat type or latitude (black line, N=196 food webs). See Fig.~\ref{TL_rescaled} to compare with 
observed values correcting for the effects of habitat type and latitude. }
\label{TL_observed}
\end{figure}

@@

@@

\begin{figure}[h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
intermediate consumers (black line) with its 95\% confidence interval (in grey), based on 
N=196 empirical food webs. Latitude is given in degrees
from the equator regardless of direction.}
\label{I}
\end{figure}

>>>>

    None of our models were greatly affected by the removal of any single food web
    or by the removal of a set of webs compiled by a common author (or group of
    authors).
    Estimates of coefficients from all jackknifed datasets were extremely
    similar (Figs.~\ref{LS_web},\ref{Gen_web},\ref{Vul_web},\ref{LS_auth},\ref{Gen_auth},\ref{Vul_auth}). 
    We are therefore very confident that, while there are undoubtedly differences 
    in the methods used to compile food webs, these differences do not explain the trends we report.

@@

    \begin{figure}[!h]
    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/LS_author.eps}}
    \caption{Estimates of the coefficients for scaling of link density with species richness
    in equation 5 (main text) do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the pseudovalues for each coefficient
    in the equation after the removal of all webs compiled by each author (or set of authors where
    multiple authors compiled identical sets of webs) in the dataset. Authors
    who compiled only a single web were jackknifed as part of the by-web jackknife.
    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line, and
    the number of webs removed in each jackknife is given in parentheses.}
    \label{LS_auth}
    \end{figure}

@@

    \begin{figure}[!h]
    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/Gen_author.eps}}
    \caption{Estimates of the coefficients for scaling of generality with species richness
    (see equation 5, main text) do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the pseudovalues for each coefficient
    in the equation after the removal of all webs compiled by each author (or set of authors where
    multiple authors compiled identical sets of webs) in the dataset. Authors
    who compiled only a single web were jackknifed as part of the by-web jackknife.
    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line, and
    the number of webs removed in each jackknife is given in parentheses.}
    \label{Gen_auth}
    \end{figure}

@@

    \begin{figure}[!h]
    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/Vul_author.eps}}
    \caption{Estimates of the coefficients for the scaling of vulnerability with species richness
    (see equation 5, main text) do not vary significantly
    when jackknifing across authors of the published food webs used in this study. 
    We show the pseudovalues for each coefficient
    in the equation after the removal of all webs compiled by each author (or set of authors where
    multiple authors compiled identical sets of webs) in the dataset. Authors
    who compiled only a single web were jackknifed as part of the by-web jackknife.
    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line, and
    the number of webs removed in each jackknife is given in parentheses.}
    \label{Vul_auth}
    \end{figure}

@@

\begin{figure}[!h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/scaling_with_S/proportions/TL_fitlines_nonts_observed.eps}}
\caption{Scaling relationships for link density, generality, 
and vulnerability relative to the proportions of basal resources, intermediate consumers, and top predators in a food web. 
For each relationship, we show observed values (white circles) and 
a simplified form of the scaling relationship described in equation 2 (\emph{Main Text}), neglecting 
any effects of habitat type or latitude (black line, N=196 food webs). See Fig.~\ref{TL_rescaled} to compare with 
observed values correcting for the effects of habitat type and latitude. }
\label{TL_observed}
\end{figure}

@@

\begin{figure}[!h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
intermediate consumers (black line) with its 95\% confidence interval (in grey), based on 
N=196 empirical food webs. Latitude is given in degrees
from the equator regardless of direction.}
\label{I}
\end{figure}

@@
